\documentclass{muratcan_coverletter}

\setname{Josh W.}{Day}
\setaddress{Pasadena, CA}
\setmobile{916.765.9396}
\setmail{jwday.work@gmail.com}
% \setposition{Work Student} %ignored for now
\setlinkedinaccount{https://www.linkedin.com/in/joshwday/} 
\setgithubaccount{https://github.com/jwday}
\setthemecolor{orange} %you can play with color of the template (red is also nice..)

\begin{document}
%Set variables
%You can add sections, texts, explanations just by copying the style below. Replace the dummy texts "\lipsum[1][x-x]\par" with actual texts.
%Create header
\headerview
\vspace{1ex}
%Sections
%
\setcompanyname{Zipline}
\setclaimedposition{Hardware Test Automation Engineer} 
\setcontactperson{} %disregard, currently using "To Whom It May Concern" in template
\coverletter{ %
% \indent \lipsum[1][1-20] %replace this part with actual text
\\
\indent It's my sincere hope that this letter does not go unread because I would genuinely like to express my interest in working with the engineering team at Zipline.
I am coming at this from a very recent upset and transformation in my life and career after congressional budget cuts forced the removal of my position at NASA's Jet Propulsion Laboratory pending restructuring of the Mars Sample Return program.
I spent the majority of my life aiming to work at NASA because I believe in working for greater good in the world, and that dream came to an abrupt halt only a few short years after it began.
After the dust settled, I realized that there existed other opportunities for me to apply my broad experience and skills as a mechanical \& aerospace engineer to make a positive impact on society.
\\

What my resume does not illustrate is the effort I was putting in to pivoting away from hardware and towards more programming-heavy responsibilities.
While I did spend much of my time working on hardware design and testing for Mars Sample Return and Europa Clipper, I also supported multiple test beds by developing data processing and test data visualization tools.
Additionally, I had submitted an abstract to the Aerospace Mechanisms Symposium outlining work I did to model and simulate the dynamic motion of a release mechanism to study a race condition which would have potentially jammed the mechanism during release if designed improperly.
Likewise, I was in the process of getting my foot in the door in JPL's Inner Planet Navigation group where I would have leveraged my Python and Kalman Filtering experience to support currently-flying missions.
\\

In addition to the aforementioned, outside of my technical background, I maintain a strong connection with my community.
Having been raised in the Sacramento area, and as an Eagle Scout in the Boy Scouts of America, I developed a love for being outdoors and a familiarity with the natural beauty that surrounds the Bay Area.
While living in Pasadena, I co-captained JPL's volleyball team in three years of the Aerospace Summer Games and have built a wonderful community of friends in the process.
\\

This is all to say that I believe my breadth of experience and personality, both in and out of the office, makes me a strong candidate for the role.
Coupled with the fact that I am strongly driven to use my chosen field make a positive contribution to the well-being of others, I am confident that I would make a valuable addition to the team at Zipline.
\\

Thank you for your consideration.
\\

-- Josh Day
% \lipsum[2][1-20]  %replace this part with actual text
}
%Footnote
\createfootnote
\end{document}
